---
title: "Barplots"
author: "Kyle Rodriguez"
date: "1/17/2022"
output: html_document
---

```{r}
library(dplyr)
library(tidyverse)
library(plotly)
library(ggplot2)
library(RColorBrewer)
library(cowplot)
library(data.table)
library(scales)
library(plotly)
```

## Barplots
```{r}
GSS2018 <- read.csv('C:/Users/rodri/Desktop/NCFS2/DataVis/Datasets/GSS2018.csv')

```

```{r}
GSS2018.pray <- GSS2018 %>% select(pray) %>% mutate(pray=as.factor(pray)) %>% drop_na() %>% count(pray)%>% mutate(precent=100*n/sum(n))
GSS2018.pray

``` 

```{r}
mycols <- brewer.pal(6,'Set2')
ggplot(data=GSS2018.pray,aes(x=pray,y=precent, fill= pray))+
  geom_bar(stat='identity') + 
  guides(fill='none')+ 
  labs(x="",y="Percent (%)",title="Frequency of Praying") + 
  scale_x_discrete(labels=c('Several Times \nPer Day','Once Per Day','Several Times \nPer Week','Once Per Week','Less Than \nOnce Per Week','Never')) +
  scale_y_continuous(expand=c(0,0)) +
  theme_classic()+ scale_fill_manual(values=mycols)+
  theme(plot.title = element_text(hjust = 0.5))